\documentclass[10pt,a4paper,ragged2e]{altacv}
\geometry{left=2cm,right=10cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1.25cm,bottom=1.25cm}
\ifxetexorluatex
  \setmainfont{Carlito}
\else
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage[default]{lato}
\fi
\definecolor{VividPurple}{HTML}{000000}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{2E2E2E}
\colorlet{heading}{VividPurple}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}
\addbibresource{sample.bib}

\begin{document}
\name{SHREYANSH SINGH}
\tagline{}
\personalinfo{%
  % Format to add more: \printinfo{symbol}{detail}
  \email{shreyansh.singh.157@gmail.com}
  \phone{+91 6393764717}
  \location{Jhansi, Uttar Pradesh - India}
 % \homepage{website link}
  % \linkedin{linkedin profile link}
}

\begin{fullwidth}
\makecvheader
\end{fullwidth}

\AtBeginEnvironment{itemize}{\small}

\cvsection[page1sidebar]{About Me}
\begin{itemize}
\item Dual postgraduate in MCA and MBA (Finance Management), combining technical and business expertise
\smallskip
\item Hands-on experience as a Frontend Developer Intern, skilled in WordPress, Shopify, and modern web technologies
\smallskip
\item Passionate about web development, AI/ML, and emerging technologies, with a focus on continuous learning and innovation.
 \end{itemize}
\smallskip

\cvsection{Experience}

\cvevent{Front End Developer (Intern)}{Graduo Pvt. Ltd.}{Aug 2023 -- Jan 2024}{Remote (Noida, Uttar Pradesh)}
\begin{itemize}
\item Built responsive front-end interfaces with modern web technologies.
\smallskip
\item Customized WordPress and Shopify themes and enhanced UI/UX with Figma.
\smallskip
\item Optimized site performance and SEO, ensuring faster load times and better visibility. 
\smallskip
\item Collaborated with clients and team members to deliver solutions aligned with business goals.
\end{itemize}
\smallskip

% \divider

\cvsection{TECHNICAL SKILLS}
\smallskip
\begin{itemize}
\item \textbf{Programming Languages: }Python, JavaScript, C, C+
\smallskip
\item \textbf{Web Development: }React.js, Node.js, Express.js, HTML5, CSS3, JS, Bootstrap, Tailwind
\smallskip
\item \textbf{Databases: }MySQL, PostgreSQL, MongoDB
\smallskip
\item  \textbf{Tools \& Platforms:} Git, GitHub, WordPress, Shopify, Figma 
\smallskip
\item \textbf{Databases: }MySQL, PostgreSQL, MongoDB
\smallskip
\item \textbf{Other Skills:} REST APIs, DSA (Basic), Financial Analysis \& Management 
\smallskip


\end{itemize}
\cvsection{SOFT SKILLS}
\smallskip
\begin{itemize}
\item Strong communication and collaboration skills.
\smallskip
\item Problem-solving and analytical thinking.
\smallskip
\item Adaptability and quick learning.
\smallskip
\item Time management and organizational ability.
\smallskip
\item Attention to detail and creativity.
\smallskip
\end{itemize}

\cvsection{Hobbies}
\smallskip
\begin{itemize}
\item Playing strategy games \& solving puzzles.
\smallskip
\item Listening to Music.
\smallskip
\item Traveling \& Exploring Cultures
\end{itemize}

\clearpage




\end{document}
