
\cvsection{Education}
\cvevent{MCA 7.5 CGPA}{Indira Gandhi National Open University}{ July 2023 -- Currently}{}
\cvevent{MBA (FM) 7.4 CGPA}{Bundelkhand University}{ July 2023 -- Currently}{}
\cvevent{B.Com 7.1 CGPA}{Bundelkhand University}{ July 2020 -- July 2023 }{}

\cvsection{Projects}
\cvproject{E-Commerce Platform}
\begin{itemize}
\item Developed a full-stack online store with product catalog, cart, checkout, and secure authentication. Used \textbf{React, Tailwind, and PostgreSQL} to build responsive UI components, manage orders in the database. 
\end{itemize}
\smallskip
\smallskip
\cvproject{Task Manager Application}
\begin{itemize}
\item Built a responsive web app to manage tasks with features such as create / update / delete, deadlines, and categorization. Implemented dashboards and user authentication with \textbf{React, Node.js, and PostgreSQL}, ensuring smooth user experience and efficient data management. 
\end{itemize}
\smallskip
\smallskip
\cvproject{AI-Powered Resume Analyzer }
\begin{itemize}
\item Created a tool that parses resumes, extracts key skills, and compares them with job descriptions. Applied \textbf{Python and NLP} to highlight keyword gaps, providing structured feedback to help candidates improve job applications. 
\end{itemize}
\smallskip
\smallskip

\cvsection{Certifications}
\smallskip
    \begin{itemize}
        \item \textbf{Deloitte Virtual Internship} – Data Analytics
\smallskip
        \item \textbf{Udemy} - The Complete Full-Stack Web Development Bootcamp (by Dr. Angela Yu)
\smallskip
\item \textbf{Udemy} - 100 Days of Code: The Complete Python Bootcamp (by Dr. Angela Yu)
\smallskip
        \item \textbf{freeCodeCamp} – Machine Learning with Python
    \end{itemize}
\smallskip
\smallskip

\cvsection{Languages}
\begin{itemize}
\smallskip
    \item \textbf{Hindi }(Native)
\smallskip
    \item \textbf{English }(Fluent)
\smallskip
\end{itemize}

\cvproject{}